# Base Case Operating Model {#sec-basecaseOM}

```{r}
#| include: false
rnorm(5)
library(MSEtool)
library(iotcALB)
library(ggplot2)
```

The Base case OM (OM5b) uses the LL1 (NW) CPUE series as the index of abundance as the primary data used in the OM conditioning (see @sec-omOverview).

The figures below show the historical dynamics of the `OM5b`, the Base Case OM:

 - female spawning biomass (@fig-om5b-ssb);
 - biomass and spawning biomass relative to unfished levels (@fig-om5b-biomass-rel, @fig-om5b-ssb-rel);
 - spawning biomass relative to the equilibrium spawning biomass corresponding with maximum sustainable yield (@fig-om5b-ssb-rel-msy); 
 - total catch summed over stocks and fleets (@fig-om5b-catch).

In each figure, the black line shows the median across simulations and the grey ribbon the 5th–95th percentile interval. 

```{r load-om5b}
#| echo: false
Hist <- readRDS('../objects/Hist/OM5b.hist')
```

```{r}
#| echo: false
#| label: fig-om5b-ssb
#| fig-cap: "Spawning biomass (SSB) from the Base Case `OM5b`. Black line is the median and the grey ribbon the 5th–95th percentile interval across simulations."
PlotSBiomass(Hist, Season = 3, Stock = 1)
```

```{r}
#| echo: false
#| label: fig-om5b-biomass-rel
#| fig-cap: "Total biomass relative to unfished biomass (B/B0), by stock, from the Base Case `OM5b`. Black line is the median and the grey ribbon the 5th–95th percentile interval across simulations."
PlotBiomass(Hist, Season = 3, byStock = TRUE, relative = "B0") 
```

```{r}
#| echo: false
#| label: fig-om5b-ssb-rel
#| fig-cap: "Female spawning biomass relative to unfished spawning biomass (SSB/SB0) from the Base Case `OM5b`. Black line is the median and the grey ribbon the 5th–95th percentile interval across simulations."
PlotSBiomass(Hist, Season = 3, Stock = 'Female', relative = "B0") 
```

```{r}
#| echo: false
#| label: fig-om5b-ssb-rel-msy
#| fig-cap: "Female spawning biomass relative to equilbrium spawning biomass at MSY (SSB/SBMSY) from the Base Case `OM5b`. Black line is the median and the grey ribbon the 5th–95th percentile interval across simulations."
PlotSBiomass(Hist, Season = 3, Stock = 'Female', relative = "BMSY")
```

```{r}
#| echo: false
#| label: fig-om5b-catch
#| fig-cap: "Total catch, summed over stocks and fleets, from the Base Case `OM5b`. Black line is the median and the grey ribbon the 5th–95th percentile interval across simulations."
t <- PlotLandings(Hist, AggregateYear = TRUE, byFleet = FALSE, byStock = FALSE)
t + ggplot2::labs(y='Catch')
```

## Comparision with Conditioning Model {#sec-basecaseCompare}

The figures below compare the Base Case OM dynamics against the ABC conditioning model across 500 MCMC simulations. In each ribbon plot, the line shows the posterior median and the shaded band the 10th–90th percentile interval for the ABC model (red) and the OM (blue). The ratio plots show OM / ABC for each individual simulation, with the dashed red line at 1 indicating perfect agreement.

```{r compareOM}
#| echo: false
#| cache: true
comp <- ValidateOM(Hist, verbose = FALSE, save_plots = FALSE)
```

### Total Numbers

```{r}
#| echo: false
#| label: fig-n-ribbon
#| fig-cap: "Total numbers: posterior median and 10–90th percentile interval for the ABC conditioning model (red) and the Base Case OM (blue)."
comp$plots$number_ribbon
```

```{r}
#| echo: false
#| label: fig-n-ratio
#| fig-cap: "Ratio of OM to conditioning model total numbers by simulation. Lines close to 1 indicate good agreement; divergence in later years reflects compounding of the Baranov vs. pulse fishing discrepancy (see @sec-differences)."
comp$plots$number_ratio
```

### Spawning Biomass

```{r}
#| echo: false
#| label: fig-ssb-ribbon
#| fig-cap: "Female spawning biomass (SSB): posterior median and 10–90th percentile interval for the ABC conditioning model (red) and the Base Case OM (blue)."
comp$plots$ssb_ribbon
```

```{r}
#| echo: false
#| label: fig-ssb-ratio
#| fig-cap: "Ratio of OM to the ABC conditioning model female spawning biomass by simulation."
comp$plots$ssb_ratio
```

### Catch by Fleet

```{r}
#| echo: false
#| label: fig-catch-ribbon
#| fig-cap: "Catch by fleet: posterior median and 10–90th percentile interval for the ABC conditioning model (red) and the Base Case OM (blue)."
comp$plots$catch_ribbon
```

```{r}
#| echo: false
#| label: fig-catch-ratio
#| fig-cap: "Ratio of OM to ABC conditioning model catch by fleet and simulation. A consistent negative bias is expected due to the Baranov equation attributing a larger share of total mortality to natural causes relative to the pulse fishing approach (see @sec-differences)."
comp$plots$catch_ratio
```

### Numbers-at-Age

```{r}
#| echo: false
#| label: fig-natage-ratio
#| fig-cap: "Ratio of OM to the ABC conditioning model numbers-at-age by simulation. Values close to 1 indicate good agreement; deviation from 1 reflects the cumulative effect of the Baranov vs. pulse fishing discrepancy."
comp$plots$natage_ratio
```
