---
suppress-bibliography: true
---

# Performance Metrics {#sec-performance-metrics}

```{r}
#| include: false
library(MSEtool)
OM <- readRDS("../objects/OM/OM5b.om")

# reference levels, as set in analysis/02-define-CMPs.R (tuning) and
# analysis/04-make-slick.R (performance metrics)
Assigned <- function(File, Names) {
  for (e in parse(File))
    if (is.call(e) && identical(e[[1]], as.name("<-")) && is.name(e[[2]]) &&
        as.character(e[[2]]) %in% Names)
      eval(e, envir = globalenv())
}
Assigned("../analysis/02-define-CMPs.R", c("PGKMin", "PSafety", "TACChange", "TACChangeDown", "nSimTune"))
Assigned("../analysis/04-make-slick.R", c("SBLim", "FLim"))

MPYears <- seq(MPStartYear(OM), by = 1, length.out = max(floor(Years(OM, "P"))) - MPStartYear(OM) + 1)
TuneYears <- utils::tail(MPYears, 15)
SafetyYears <- MPYears[-seq_len(5)]   # MSEtool::PMYears(OM, Skip = 5)
Windows <- list(Short  = utils::head(MPYears, 10),
                Medium = setdiff(MPYears, c(utils::head(MPYears, 10), utils::tail(MPYears, 10))),
                Long   = utils::tail(MPYears, 10))
yr_range <- function(x) paste(range(x), collapse = "--")

SlickFile <- "../objects/slick.rds"
HasSlick  <- file.exists(SlickFile)
if (HasSlick) slick <- readRDS(SlickFile)
```

## Management Objectives

The IOTC has adopted interim target and limit reference points for albacore: targets of SB~MSY~ and F~MSY~, and limits of `r SBLim` SB~MSY~ and `r FLim` F~MSY~ [@IOTCRes1510]. As SB~MSY~ is less than 20% of SB~0~ in the OMs, the limit reference point corresponds to less than 10% of SB~0~ (@sec-om-status), and therefore performance relative to SB~0~ is also reported.

Consistent with the tuning objectives used for the earlier albacore MSE work [@mosqueiraTechnicalDevelopmentManagement; @mosqueira2026albacore], the CMPs are evaluated against the following candidate management objectives:

1.  **Status:** Maintain the stock in the green quadrant of the Kobe plot (SB \> SB~MSY~ and F \< F~MSY~) with at least `r 100 * PGKMin`% probability;
2.  **Safety:** Spawning biomass should not fall below the limit reference point, with at least `r 100 * PSafety`% probability, and fishing mortality should be below the limit reference point with a high probability;
3.  **Yield:** Maximise catches;
4.  **Stability:** Changes in the TAC between management periods should be relatively gradual.

The CMPs are tuned for the Base Case OM to maximise the mean annual catch over the years the CMPs are active (`r yr_range(MPYears)`), at two tuning levels (@sec-tuning-methodology):

1.  *T1*: a probability of at least `r PGKMin` of being in the Kobe green quadrant over the last 15 years of the projection period (`r yr_range(TuneYears)`);

2.  *T2*: the *T1* constraint plus a requirement of a probability of at least `r PSafety` that spawning biomass stays above the LRP (`r SBLim` SB~MSY~) in every year over `r yr_range(SafetyYears)`.

```{r}
#| echo: false
#| label: tbl-pm-summary
#| tbl-cap: "The candidate management objectives and the corresponding performance metrics."
PMTab <- data.frame(
    Category  = c(rep('Status', 4), rep('Safety', 3), rep('Yield', 2), rep('Stability', 2)),
    Objective = c(paste0('Maintain the stock in the Kobe green quadrant with at least ', 100 * PGKMin, '% probability'), '', '', '',
                  paste0('SB should not fall below the LRP, with at least ', 100 * PSafety, '% probability, and F should be below the limit with high probability'), '', '',
                  'Maximise catches', '',
                  'Change in TAC between management periods should be relatively gradual', ''),
    Metric    = c(paste0('Probability that SB > SB~MSY~ and F < F~MSY~ over ', yr_range(TuneYears), ' (tuning constraint, T1 and T2), over ', yr_range(MPYears), ', and in each time window'),
                  'Probability that SB < SB~MSY~ and F > F~MSY~ (Kobe red quadrant)',
                  'Mean SB/SB~MSY~ and mean F/F~MSY~',
                  'Minimum SB/SB~MSY~',
                  paste0('Probability that SB > ', SBLim, ' SB~MSY~ in every year over ', yr_range(SafetyYears), ' (tuning constraint, T2)'),
                  paste0('Probability that SB > ', SBLim, ' SB~MSY~ (proportion of simulations and years)'),
                  paste0('Probability that F < ', FLim, ' F~MSY~'),
                  paste0('Mean annual catch over ', yr_range(MPYears), ' (maximised in tuning)'),
                  'Mean annual catch in each time window',
                  'Mean absolute proportional change in the TAC between management periods',
                  'Probability that the TAC change limit is binding')
  )
# HTML table (kableExtra), so markdown is converted by hand: subscripts, comparison signs, and dashes
Sub <- function(x) {
  x <- gsub(' < ', ' &lt; ', gsub(' > ', ' &gt; ', x, fixed = TRUE), fixed = TRUE)
  x <- gsub('--', '&ndash;', x, fixed = TRUE)
  gsub('~([A-Za-z0-9]+)~', '<sub>\\1</sub>', x)
}
PMTab$Objective <- Sub(PMTab$Objective)
PMTab$Metric    <- Sub(PMTab$Metric)
Groups <- rle(PMTab$Category)
kt <- knitr::kable(PMTab[, c('Objective', 'Metric')], format = 'html', escape = FALSE, row.names = FALSE,
                   col.names = c('Management Objective', 'Performance Metric')) |>
  kableExtra::kable_styling(bootstrap_options = c('striped', 'condensed'), full_width = TRUE)
Start <- 1
for (i in seq_along(Groups$values)) {
  kt <- kableExtra::pack_rows(kt, Groups$values[i], Start, Start + Groups$lengths[i] - 1,
                              label_row_css = 'font-weight: bold; border-bottom: 1px solid #ddd;')
  Start <- Start + Groups$lengths[i]
}
kt
```

## Performance Metrics

All performance metrics are calculated over the `r length(MPYears)` years in which the CMPs set the TAC (`r yr_range(MPYears)`), unless a different set of years is specified, for each OM and CMP. The following notation is used:

- $s = 1, \ldots, S$ indexes the simulations and $y \in \mathcal{Y}$ the $N_Y$ years;
- $SB_{s,y}$ is the female spawning biomass in the reference season of year $y$;
- $F_{s,y}$ is the annual apical fishing mortality, summed over the quarters of year $y$, on the same basis as F~MSY~;
- $C_{s,y}$ is the annual catch (total removals of all fleets, in t);
- $\text{TAC}_{s,c}$ is the TAC set in management cycle $c = 1, \ldots, N_C$, where $\text{TAC}_{s,0}$ is the TAC (catch) in the year before the first management cycle, $\Delta_{s,c} = \lvert \text{TAC}_{s,c} - \text{TAC}_{s,c-1} \rvert / \text{TAC}_{s,c-1}$ is the relative change in the TAC, and $\delta_{s,c}$ is the maximum TAC change allowed by the CMP in the direction of the change (increases: `r paste0(100 * TACChange, '%')`; decreases: `r paste0(100 * TACChangeDown[['T1']], '%')` for T1 and `r paste0(100 * TACChangeDown[['T2']], '%')` for T2);
- $\mathrm{I}(\cdot)$ is 1 if the condition is true and 0 otherwise.

### Status

The probability of being in the green quadrant of the Kobe plot:

$$
P_{\text{Kobe}} = \frac{1}{S N_Y} \sum_{s} \sum_{y} \mathrm{I}\left(\frac{SB_{s,y}}{SB_{\text{MSY}}} > 1 \ \text{and} \ \frac{F_{s,y}}{F_{\text{MSY}}} < 1\right)
$$ {#eq-pgk}

calculated for all years the CMPs are active (`r yr_range(MPYears)`), the tuning period (`r yr_range(TuneYears)`), and each time window (@sec-pm-windows). The other Status metrics are calculated over all years the CMPs are active (`r yr_range(MPYears)`).

The probability of being in the red quadrant:

$$
P_{\text{Red}} = \frac{1}{S N_Y} \sum_{s} \sum_{y} \mathrm{I}\left(\frac{SB_{s,y}}{SB_{\text{MSY}}} < 1 \ \text{and} \ \frac{F_{s,y}}{F_{\text{MSY}}} > 1\right)
$$ {#eq-pred}

The mean SB/SB~MSY~:

$$
\overline{SB/SB_{\text{MSY}}} = \frac{1}{S N_Y} \sum_{s} \sum_{y} \frac{SB_{s,y}}{SB_{\text{MSY}}}
$$ {#eq-sbmean}

the mean F/F~MSY~:

$$
\overline{F/F_{\text{MSY}}} = \frac{1}{S N_Y} \sum_{s} \sum_{y} \frac{F_{s,y}}{F_{\text{MSY}}}
$$ {#eq-fmean}

and the minimum SB/SB~MSY~ over the years the CMPs are active in each simulation, $\min_{y} SB_{s,y}/SB_{\text{MSY}}$.

### Safety

The probability that spawning biomass does not fall below the limit reference point (`r SBLim` SB~MSY~; @IOTCRes1510) in any year; i.e., the proportion of simulations in which spawning biomass is above the LRP in every year over `r yr_range(SafetyYears)`:

$$
P_{\text{Safety}} = \frac{1}{S} \sum_{s} \mathrm{I}\left(\min_{y \in \mathcal{Y}_{\text{S}}} \frac{SB_{s,y}}{SB_{\text{MSY}}} > `r SBLim`\right)
$$ {#eq-safety}

where $\mathcal{Y}_{\text{S}}$ are the years `r yr_range(SafetyYears)`. A single year below the LRP is a breach. This is the safety constraint of tuning level **T2**.

The first 5 years the CMPs are active are excluded, so that the stock can recover from the catches of the initial projection years, which are not controlled by the CMPs (@sec-tuning-methodology).

The probabilities that spawning biomass is above, and fishing mortality is below, the limit reference points (`r SBLim` SB~MSY~ and `r FLim` F~MSY~), as the proportion of simulations and years, are also reported:

$$
P_{SB_{\text{lim}}} = \frac{1}{S N_Y} \sum_{s} \sum_{y} \mathrm{I}\left(\frac{SB_{s,y}}{SB_{\text{MSY}}} > `r SBLim`\right)
$$ {#eq-sblim}

and

$$
P_{F_{\text{lim}}} = \frac{1}{S N_Y} \sum_{s} \sum_{y} \mathrm{I}\left(\frac{F_{s,y}}{F_{\text{MSY}}} < `r FLim`\right)
$$ {#eq-flim}

### Yield

The mean annual catch:

$$
\bar{C} = \frac{1}{S N_Y} \sum_{s} \sum_{y} C_{s,y}
$$ {#eq-yield}

calculated over all years the CMPs are active and each time window.

### Stability

The mean absolute proportional change in the TAC between management cycles:

$$
\text{AAV} = \frac{1}{S N_C} \sum_{s} \sum_{c} \Delta_{s,c}
$$ {#eq-aav}

and the probability that the TAC change limit is binding:

$$
P_{\delta} = \frac{1}{S N_C} \sum_{s} \sum_{c} \mathrm{I}\left(\Delta_{s,c} \geq \delta_{s,c}\right)
$$ {#eq-taclimited}

As all CMPs limit TAC increases to `r paste0(100 * TACChange, '%')`, and the *T1* CMPs also limit decreases to `r paste0(100 * TACChangeDown[['T1']], '%')`, the probability that the TAC changes by no more than `r paste0(100 * TACChange, '%')` is not reported. The larger decreases allowed in the *T2* CMPs are reflected in the mean TAC change.

## Time Windows {#sec-pm-windows}

The probability of being in the Kobe green quadrant and the mean catch are also calculated for three time windows:

1.  **Short**: the first 10 years (`r yr_range(Windows$Short)`);
2.  **Medium**: the second 10 years (`r yr_range(Windows$Medium)`);
3.  **Long**: the last 10 years (`r yr_range(Windows$Long)`).

## Summary of Performance Metrics

The performance metrics reported for every CMP and OM combination are listed in @tbl-pm-all.

```{r}
#| echo: false
#| label: tbl-pm-all
#| tbl-cap: "Performance metrics computed for every CMP and OM combination."
#| eval: !expr HasSlick
bp <- slick@Boxplot
# plain-text labels from the Slick object: HTML subscripts, comparison signs, and year ranges
Fmt <- function(x) {
  x <- gsub('<', '&lt;', gsub('>', '&gt;', x, fixed = TRUE), fixed = TRUE)
  x <- gsub('\\b(SB|F|B)(MSY|0)\\b', '\\1<sub>\\2</sub>', x, perl = TRUE)
  gsub('([0-9]+)-([0-9]+)', '\\1&ndash;\\2', x)
}
knitr::kable(
  data.frame(Label = Fmt(Slick::Label(bp)), Description = Fmt(Slick::Description(bp))),
  format = 'html', escape = FALSE, row.names = FALSE,
  col.names = c('Metric', 'Description')
) |>
  kableExtra::kable_styling(bootstrap_options = c('striped', 'condensed'), full_width = TRUE) |>
  kableExtra::column_spec(1, width_min = '15em')
```

```{r}
#| echo: false
#| results: asis
if (!HasSlick)
  cat("*The table of performance metrics will be added once the results are available.*")
```
